Pigeons.jl: Distributed sampling from intractable distributions

### 2025-05-06 workshop/paper.tex
first attempt @ icml workshop (broken)

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

@@

@@

\input{header}

\maketitle

\begin{abstract}
We introduce a software package, Pigeons.jl, that provides a way to leverage distributed computation to 
obtain samples from complicated probability distributions, such as 
multimodal posteriors arising in Bayesian inference and high-dimensional 
distributions in statistical mechanics. Pigeons.jl provides a simple user interface to 
perform such computations single-threaded, multi-threaded,
and/or distributed over thousands of MPI-communicating machines.
In addition, Pigeons.jl guarantees a property that we call strong parallelism invariance: the 
output for a given seed is identical irrespective of the number of threads and processes, 
which is crucial for scientific reproducibility and software validation. 
We describe the key features of Pigeons.jl and the approach taken to implement 
a distributed and randomized algorithm that satisfies strong parallelism invariance.
\end{abstract}

\input{introduction.tex}
\input{examples.tex}
\input{PT.tex}
\input{SPI.tex}
\input{related.tex}
\input{conclusion.tex}

\section{Acknowledgements}
NS acknowledges the support of a Vanier Canada Graduate Scholarship. 
PT acknowledges the support of the Black Hole Initiative at Harvard University, 
which is funded by grants from the John Templeton Foundation and the 
Gordon and Betty Moore Foundation to Harvard University.
PT also acknowledges support by the National Science Foundation grants AST-1935980 
and AST-2034306 and the Gordon and Betty Moore Foundation (GBMF-10423).
SS acknowledges the support of EPSRC grant EP/R034710/1 CoSines.
ABC and TC acknowledge the support of an NSERC Discovery Grant.
We also acknowledge use of the ARC Sockeye computing platform from the
University of British Columbia, as well as cloud computing resources provided 
by Oracle.

\input{bib.tex}

>>>>

\documentclass{article}

\usepackage[accepted]{icml2025}
\usepackage{listings}
\usepackage{jlcode}
\usepackage{natbib}
\setcounter{page}{1}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Pigeons.jl: Distributed sampling from intractable distributions}

@@

\twocolumn[
\icmltitle{Pigeons.jl: Distributed sampling from intractable distributions}

\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Nikola Surjanovic}{ubc}
\icmlauthor{Miguel Biron-Lattes}{sfu}
\icmlauthor{Paul Tiede}{harvard}
\icmlauthor{Saifuddin Syed}{oxford}
\icmlauthor{Alexandre Bouchard-C{\^o}t{\'e}}{ubc}
\icmlauthor{Trevor Campbell}{ubc}
\end{icmlauthorlist}

\icmlaffiliation{harvard}{Center for Astrophysics, Harvard University, United States}
\icmlaffiliation{oxford}{Department of Statistics, University of Oxford, United Kingdom}
\icmlaffiliation{sfu}{Department of Statistics and Actuarial Sciences, Simon Fraser University, Canada}
\icmlaffiliation{ubc}{Department of Statistics, University of British Columbia, Canada}

\icmlcorrespondingauthor{Miguel Biron-Lattes}{mbironla@sfu.ca}
\icmlkeywords{Distributed computation, Bayesian inference, Markov chain Monte Carlo, Parallelism Invariance, Message Passing Interface, Multi-Threading}

\vskip 0.3in
]

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution

\input{abstract}
\input{introduction.tex}
\input{examples.tex}
\input{PT.tex}
\input{SPI.tex}
\input{related.tex}
\input{conclusion.tex}
\input{ack}

\bibliographystyle{icml2025}
\bibliography{../paper/ref.bib}
